\mutagen: Coverage-Guided, Property-Based Testing using Exhaustive Structure-Preserving Mutations

### 2022-03-02 papers/fse22/main.tex
Added FSE22 initial version
Compressed abstract

%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf, review]{acmart}

@@

%% These commands are for a JOURNAL article.
\acmConference[AST 2022]{3rd ACM/IEEE International Conference on Automation of Software Test}{May 21-22, 2022}{}

%% \acmJournal{JACM}
%% \acmVolume{37}
%% \acmNumber{4}
%% \acmArticle{111}
%% \acmMonth{8}

@@

\begin{abstract}
Automatically synthesized random data generators are an appealing option when
using property-based testing.
%
Such generators can be obtained using a variety of techniques that extract
static information from the codebase in order to produce random test cases.
%
However, such techniques are not suitable for deriving generators producing
random values satisfying complex invariants, which in turn complicates testing
properties with sparse preconditions.

Coverage-guided, property-based testing (CGPT) is a recent technique that
alleviates this limitation by enhancing automatically synthesized generators
with structure-preserving mutations guided by execution traces.
%
Albeit effective, the initial CGPT approach is limited by factors like large
reliance on randomness and poor mutants scheduling, reducing its applicability
and bug-finding capacity in existing software.

In this work we present \mutagen, a CGPT framework that overcomes these
limitations by generating mutants in an \emph{exhaustive} manner.
%
This is coupled with heuristics that help to schedule mutants based on their
novelty and to minimize mutating certain subexpressions leading to scalability issues of
exhaustiveness.
%of large enumeration types more
%than necessary.
%
Our results indicate that our approach is capable of outperforming existing CGPT
tools, as well as finding bugs in real-world scenarios.
\end{abstract}

@@

\vspace{-5pt}

@@

\begin{figure}[t]
\begin{verbatim}
mutate (Leaf x) =
  [ PURE (Branch def x def) ]
mutate (Branch l x r) =
  [ PURE l, PURE r
  , PURE (Leaf x)
  , PURE (Branch l x l), PURE (Branch r x r), PURE (Branch r x l) ]
\end{verbatim}
\vspace{-5pt}
\caption{\label{fig:mutagen:mutator}\mutagen mutator for the \texttt{Tree} data
  type.}
\vspace{-5pt}
\end{figure}

>>>>

%% The first command in your LaTeX source must be the \documentclass command.
% \documentclass[sigconf, review]{acmart}
\documentclass[sigconf,review,anonymous]{acmart}

@@

%% These commands are for a JOURNAL article.
\acmConference[ESEC/FSE 2022]{The 30th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{14 - 18 November, 2022}{Singapore}
%% \acmJournal{JACM}
%% \acmVolume{37}
%% \acmNumber{4}
%% \acmArticle{111}
%% \acmMonth{8}

@@

\begin{abstract}
Automatically synthesized random data generators are an appealing option when
using property-based testing.
%
There exists a variety of techniques that extract static information from the
codebase to produce random test cases.
%
Sadly, such techniques cannot derive generators capable of producing random
values satisfying complex invariants, often needed to test properties with
sparse preconditions.

Coverage-guided, property-based testing (CGPT) is a technique that tackles this
limitation by enhancing synthesized generators with structure-preserving
mutations guided by execution traces.
%
Albeit effective, CGPT relies largely on randomness and exhibits poor
scheduling, preventing its applicability in real-world software.

This work presents \mutagen, a CGPT framework that overcomes such limitations by
generating mutants \emph{exhaustively}.
%
Our tool incorporates heuristics to help minimizing scalability issues as well
as covering the search space in a principled manner.   
%
% schedule mutants based on their
% novelty and to minimize mutating certain subexpressions leading to scalability
% issues of exhaustiveness.
%of large enumeration types more
%than necessary.
%
Our evaluation show that \mutagen not only outperforms existing CGPT tools, but
also finds previously unknwown bugs in real-world software.
\end{abstract}

@@

% \vspace{-5pt}

@@

\begin{figure}[b]
\begin{verbatim}
mutate (Leaf x) =
  [ PURE (Branch def x def) ]
mutate (Branch l x r) =
  [ PURE l, PURE r
  , PURE (Leaf x)
  , PURE (Branch l x l), PURE (Branch r x r), PURE (Branch r x l) ]
\end{verbatim}
\vspace{-5pt}
\caption{\label{fig:mutagen:mutator}\mutagen mutator for the \texttt{Tree} data
  type.}
\vspace{-5pt}
\end{figure}
